### 2025-06-12 project_Omar/paper.tex
hopefully final version

During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}
In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
On the current LHC/HL-LHC plan, Run 3 began in 2022 and is planned to last until the first half of 2026, expecting and integrated luminosity of about \lumi{500}, as seen in figure \ref{figure1}.

@@

The CMS silicon pixel detector consists of four concentric cylindrical layers and three disks on each end, placed at certain distances from the center of the detector. The detector consists of 1856 sensor modules, and gives complete coverage over the interaction point, resulting in precise tracking. This yields a large amount of total pixels, so, adding the sensor's fine granularity, the hit occupancy is very low. Due to this, the Pixel Cluster Counting (PCC) method brings forth a linear function of pile up, which is an essential property of a luminometer. The PCC method has been used as one of main luminometers for more than a decade, showing its reliability.

@@

\section{OBJECTIVE}

@@

\section{HYPOTHESIS}

Based on the analysis corresponding to previous years, a similar or better result is expected. With a systematic uncertainty of 1.4\% for 2022, and 1.3\% for 2023, it is possible to achieve a precision as good as this, if not an improvement.

\section{METHODOLOGY}

A pixel cluster is for a group of contiguous pixels activated by a charged particle. The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small, so it yields measurements with a great linear response with the pile-up (number of interactions per bunch crossing, $\mu$). To calibrate the luminometer, the van der Meer (vdM) scan technique is employed in special runs, usually at the beginning of the year or period. The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions) and callibration (or vdM) runs. As the title of the project suggests, callibration runs are the subject of study, and consist of more controlled collisions to be able to determine luminosity from the beam parameters.

% vdm graph

During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs. The data is then distributed in 32 different datasets of events. %referencia pa la imagen de pile-up en runs de fisica

@@

\begin{center}
  $\int\rho_1(y)\rho_2(y+\Delta y)dy=\frac{\int\mathcal{L}(\Delta x, \Delta y)d(\Delta x)}{N_1 N_2 f} \Rightarrow \mathcal{L}(\Delta x, \Delta y)=\int\rho_1(x)\rho_2(x+\Delta x)dx\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')$
\end{center}

@@

The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year. In order to compute the constant, a mathematical function needs to be used to fit the averaged cluster rates, so the parameters needed, such as $\Sigma_{x,y}$ and $R(0,0)$, can be extracted.

@@

\section{SPECIFIC OBJECTIVES}

@@

\section{EXPECTED RESULTS}

@@

\section{CALENDAR OF ACTIVITIES}

@@

\onehalfspacing
\bibliographystyle{unsrt} % y esto...........
\bibliography{paper}

>>>>

During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}
In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with a precision of 1.3\% \cite{Sirunyan:2021qkt}.
For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
On the current LHC/HL-LHC plan, Run 3 began in 2022 and is planned to last until the first half of 2026, expecting and integrated luminosity of about \lumi{500}, as seen in figure \ref{figure1}.

@@

The CMS silicon pixel detector consists of four concentric cylindrical layers and three disks on each end, placed at certain distances from the center of the detector. The detector consists of 1856 sensor modules, and gives complete coverage over the interaction point, resulting in precise tracking \cite{TrackerGroupoftheCMS:2020bgg}. This yields a large amount of total pixels, so, adding the sensor's fine granularity, the hit occupancy is very low. Due to this, the Pixel Cluster Counting (PCC) method brings forth a linear function of pile up, which is an essential property of a luminometer. The PCC method has been used as one of main luminometers for more than a decade, showing its reliability.

@@

\section{OBJECTIVE}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{HYPOTHESIS}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Based on the analysis corresponding to previous years, a similar or better result is expected. With a systematic uncertainty of 1.4\% for 2022 \cite{Collaboration:124}, and 1.3\% for 2023 \cite{CMS-DP-2024-068}, it is possible to achieve a precision as good as this, if not an improvement.

\section{METHODOLOGY}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

A pixel cluster is for a group of contiguous pixels activated by a charged particle. The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small, so it yields measurements with a great linear response with the pile-up (number of interactions per bunch crossing, $\mu$). To calibrate the luminometer, the van der Meer (vdM) scan technique is employed in special runs, usually at the beginning of the year or period \cite{CMS:2018}. The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions) and callibration (or vdM) runs. As the title of the project suggests, callibration runs are the subject of study, and consist of more controlled collisions to be able to determine luminosity from the beam parameters.

% vdm graph?

During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs \cite{eysermans_cms_mw_lowPU} \cite{cms_new_record_2024}. The data is then distributed in 32 different datasets of events.

@@

\begin{align*}
  \int\rho_1(y)\rho_2(y+\Delta y)dy &= \frac{\int\mathcal{L}(\Delta x, \Delta y)d(\Delta x)}{N_1 N_2 f}\\
  \Rightarrow \mathcal{L}(\Delta x, \Delta y) &=\int\rho_1(x)\rho_2(x+\Delta x)dx\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')
\end{align*}

@@

The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year \cite{CMS:2018}. In order to compute the constant, a mathematical function needs to be used to fit the averaged cluster rates, so the parameters needed, such as $\Sigma_{x,y}$ and $R(0,0)$, can be extracted.

@@

\section{SPECIFIC OBJECTIVES}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{EXPECTED RESULTS}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{CALENDAR OF ACTIVITIES}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\onehalfspacing
\bibliographystyle{unsrt} 
\bibliography{paper}
